% Kindle KDP Paperback, Latex using the Memoir package
% https://www.ctan.org/pkg/memoir?lang=en

% Ian Hocking, August 2017

% Usage:

% This template should generate a 5' x 8' PDF
% suitable for the interior of a paperback.
% It's intended for the Amazon Kindle Paperback programme.

% When generated*, open the PDF and delete the first, blank page,
% as well as the blank page prior to the copyright notice.
% Upload this to the KDP system and it should flow appropriately
% (with 'About the Author' being on a recto, or right-side leaf
% and chapters beginning recto too)

% Use a Latex distribution for your platform: https://www.latex-project.org 

\documentclass[postvopaper, openright, twoside, onecolumn, final]{memoir}
% postvopaper is 8x5 inch stock (untrimmed)
% openright: each chapter will start on a recto page (right hand leaf when book is open)
% twoside: document will be published with printing on both sides of paper
% onecolumn: text is one column, not multi-column
% final: finalise

% Load packages
\usepackage[T1]{fontenc}                   % Fundamental
\usepackage[latin1]{inputenc}              % For typographical accents etc.
\usepackage{lettrine}                      % For drop caps
\usepackage[ngerman,french,english]{babel}

% Set document options
\settypeblocksize{5in}{3in}{*}             % Define the 'typeblock', i.e. the area that holds the main text
\setlength\parindent{9pt}                  % Size of the paragraph indent

% The default mode for LaTeX typesetting is \fussy where the (variation of) interword spacing in justified text is kept to a minimum. Following the \sloppy declaration there may be a much looser setting of justified text. \midsloppy is between the two. So:
\midsloppy

% The following should help with widow/orphan control
\clubpenalty=10000
\widowpenalty=10000
\raggedbottom

% Header options 
\addtopsmarks{headings}{}{
  \createmark{chapter}{left}{nonumber}{}{}
}
\pagestyle{headings} % activate changes

% Suppress page numbers in front matter
\usepackage{etoolbox}
\makeatletter
\aliaspagestyle{title}{empty} % suppress the page number after \maketitle
\let\origps@chapter\ps@chapter
\preto\frontmatter{\let\ps@chapter\ps@empty\pagestyle{empty}}
\preto\mainmatter{
  \cleardoublepage
  \let\ps@chapter\origps@chapter\pagestyle{headings}}
\makeatother



% Set titling
\title{PROPER JOB}
\author{Ian M Hocking}
\date{}                  





\begin{document}

\frontmatter

% Temporary page (to be manually deleted after creating PDF)
\newpage\null\thispagestyle{empty}\newpage


% Page: About the Author
\par\vspace*{.1\textheight}{\centering \textsc{about the author}\par}
\setlength{\parskip}{10pt}                                             % changes vertical space between paragraphs
\noindent
Ian M Hocking is a university lecturer and researcher 
based in Canterbury. Three things about him. One: he 
almost vomited raw shark over the Prime Minister of 
Iceland. Two: he likes to run (for instance, away from 
Prime Ministers). Three: he spent several years 
researching this novel and wishes he hadn't.

\noindent
As Ian Hocking (sans M), he writes character-based science 
fiction thrillers with a philosophical edge. Otherwise, 
he has been known to write comedy fiction, like what this is.

\noindent
Come with him now into a world of sand, surf, and vanilla essence.

\begin{quotation}

\noindent

Like Spike Milligan---but in a good way.

\sourceatright{Mil Millington}

\end{quotation}


% Page: By Ian Hocking

\par\vspace*{.1\textheight}{\centering \textbf{By Ian Hocking}\par}
\setlength{\parskip}{10pt}
\noindent

\vspace{2mm} %2mm vertical space

\centerline{\emph{The Saskia Brandt Series}}
\vspace{2mm} 

\centerline{\textsc{déjà vu}}
\vspace{2mm}

\centerline{\textsc{flashback}}
\vspace{2mm}

\centerline{\textsc{the amber rooms}}
\vspace{2mm}

\centerline{\emph{The Agents Temporal Series}}
\vspace{2mm}

\centerline{\textsc{red star falling}}
\vspace{2mm}

\centerline{\emph{Short Stories}}
\vspace{2mm}

\centerline{\textsc{solaristics}}
\vspace{2mm}

\centerline{\emph{As Ian M Hocking}}
\vspace{2mm}

\centerline{\textsc{proper job}}


% Page: Title

\begin{titlingpage}

\maketitle

\end{titlingpage}

\newpage\thispagestyle{empty}
\null\vfill
\noindent
\setlength{\parskip}{10pt}

\begin{flushleft}Copyright (c) 2015 by Ian M Hocking

http://ianhocking.com

http://twitter.com/ian\_hocking

Unless otherwise stated, this story is a work of fiction. Names,
characters, places, and incidents are either products of the author's
imagination or used fictitiously. Any resemblance to actual events,
locales, or persons, living or dead, is entirely coincidental.

All rights reserved.

No part of this publication may be reproduced or transmitted in any form
or by any means, electronic or mechanical, without permission in writing
from the author.

Ian Hocking has asserted his right under the Copyright, Designs and
Patents Act 1988 to be identified as the author of this work.

Cover designed by the author---obviously.

Edited by Clare Christian.

Proofed by Olivia Wood.

Version 28972472
\end{flushleft}

\par\vspace*{.35\textheight}{\centering For Alvin\par}

% Parskip is the size of the gap between paragraphs. We want
% this to be zero from this point on 
\setlength{\parskip}{0\baselineskip} % Note: author of Memoir warns this may cause problems



\mainmatter

% This makes sure the gutter is larger than Memoir default
\setlrmargins{*}{*}{0.666} \checkandfixthelayout

\chapter{}

\begin{flushright}
\emph{Cornwall: Summer, 1999}
\end{flushright}

% Lettrine package handles drop cap; first brace includes drop cap;
% second brace is small caps
\lettrine{I}{ turned} nonchalantly to Old Boy. We had run all the way from his house
to St Austell's Holmbush industrial estate, and my metabolism was
halfway between aerobic and anaerobic respiration. It made nonchalance
tricky to achieve.

I'd known Old Boy since our first A-Level physics class, when, within
minutes of meeting him, I'd spilled a beaker of mercury down his leg. It
broke the ice wonderfully. Away we chatted, the two of us, until halfway
through the lesson I realised I had forgotten his name. However, we had
passed that conversational Rubicon beyond which it is simply no longer
cricket to re-enquire what your new friend is called. Months went by,
each filled with attempts to discover his name, but since he spoke to no
one but me and his suicidal dog, there was no hope of overhearing it. By
the following Easter, I had settled on `Old Boy', having worked through
the Cornish appellations `Ma'ey', `Wussnem', and `Wussicle'.

Old Boy was originally from Nottingham. His parents were bakers, and I
had convinced him to accompany me on this job interview so he could
ditch the early starts and the untold terrors of crimping elbow for a
new position doing whatever it was they did at Smart Publishing. Plus,
he could keep me company.

`Andy,' he said, `I'm getting my nervous ear.'

He pushed back a mousy lock of home-cut hair and showed me. He was
right. It was twitching.

`Easy, mate,' I said, kneading a stitch below my ribs, `easy like Sunday
morning.'

It's hard enough being seventeen, single and awkward. I could tell you
that. It's even harder being seventeen, single, awkward and Old Boy. He
could tell you that. Or, at least, he would if he could. He'd actually
be dumbfounded with awkwardness.

That's Old Boy.

Me? You know me already. I'm the nondescript who sat at the front in
double Maths and seemed gay but actually wasn't. I'm friendly enough,
but I sound like someone who has ended up at your grubby school because
he has been expelled from one where first years fag, rugby is called
rugger, and desk graffiti features Latin with properly declined verbs.

`Everything's fine,' I said. `Look, it's only 7:59.'

`You're right,' he said. The pained line of his mouth bent into a smile.
`We made it.'

`And relax,' I said.

In my head, I heard a cheerful, electronic chirrup like the sound a
computer makes when you've completed a level in a game.

\emph{Nonchalance unlocked.}

The building complex yonder---the headquarters of Smart Publishing---was
knocked down to make way for a retail park in 2008, but, in 1999, when
Old Boy and I were leaning on its gate and straightening our ties, its
complex of dirty buildings dominated the estate. An incinerator tower
was already farting its ashy nonsense into the air and it was barely 8
am. On the forecourt, men with clipboards jogged out of one door and in
another. They looked harassed and unhappy. Forklifts trundled through
curtains of plastic. Lorries queued, carrying paper rolls the size of
houses.

I took off my glasses and gave them a wipe with my handkerchief.

`Ready?' I asked.

He tried to smile. `Ready.'

`Late for the interview, isn't it?' asked a Welshman.

The sudden appearance of Mr Smart was only a whisker less unsettling
than a firecracker in a library. He looked shorter than his local TV
adverts had suggested. His age was difficult to judge. His red hair and
beard reminded me of Matthew Corbett, the bloke who made a living with
his hand up a bear puppet called Sooty. Indeed, he had the unsettling
all-purpose gusto of a 1980s science programme presenter.

`Sorry,' I said. `All these factories look alike.'

`Do I look like I want to waste time?'

`I'm sorry?'

`Stop saying that. Do I look like I want to waste time?'

I stared at him for a while. Then I said, `No?'

Before I knew it, Mr Smart was halfway across the forecourt. He made
sudden turns according to coloured lines that marked a safe route
through the traffic of forklifts and lorries. As Old Boy and I hurried
to catch up, he reached a door in the main building and swiped a card
through the lock.

He looked at me.

Nodded once.

Then he sprinted into the building with the desperate scramble of a
father who has left his infant daughter in a receding taxi.

`Puzzling,' I said.

Old Boy barged past me. `It's part of the interview, Andy! Run for it!'

I groaned.

`But I'm already sweaty.'

`The job,' returned his fading voice. `The job!'

`Nonchalantly does it, mate,' I called after him.

I walked into the building. The only remnants of Mr Smart's dash were
the tick-tock of inspirational leadership posters and a fallen plant. I
picked it up. A woman in a plain uniform emerged from the T-junction
ahead, tugging a vacuum cleaner.

She nodded at me.

I nodded back.

`Mr Smart's office?'

`Take a left here, then two rights. Go up the stairs until you're at the
top of the building.'

Very slowly, as though trying not to trip a motion sensor, I gave her
the plant.

\section*{}

Mr Smart's office had a panoramic view of St Austell Bay. His desk was
huge and looked like it could flip over to reveal a working model of his
plan to spray Bodmin with some kind of gas. He stood with his back to
the door, surveying the distant sea, hands clasped behind him. Old Boy
was standing near a bookcase at the rear of the room. He was thumbing
desperately through a catalogue.

`Tell me, Mr Carrick,' said Mr Smart. `Whatever happened to Bobby
Davro?'

`Who?'

He waited.

`I see,' I said, seeing nothing.

From there, the interview just got weird.

`Smart Publishing,' he said. `What do we do, and how do we do it, Mr
Carrick?'

To give myself time, I looked at Old Boy. He was running a finger
through the index of the catalogue. He was obviously panicking.

`Mate,' I whispered, `what are you looking for?'

`A left-handed screwdriver,' he said.

Mr Smart turned. `We publish it all here. \emph{Cows! House and Gnome.
The Periodical Review of Pugging.}'

`Sounds---niche.'

`How old are you, son?' he asked.

`Almost eighteen.'

`Seventeen, in other words.'

Fiercely, he separated the pages of my CV. Beneath them, I saw a page of
Old Boy's. I leaned forward in the hope of learning his name, but Mr
Smart put his elbows on the desk and looked at me once more.

`So, you've got a full complement of GCSEs,' he said, `all of them A
grades. Further maths, no less. Think quickly: What's eighty-six divided
by eighty-five?'

\section*{}

Factory Two was the size of our college assembly hall and just as dirty.
It had a low ceiling of asbestos tiles. Half of the floor space was
obscured with palettes of magazines and a huge contraption that was fed
by a conveyor belt. Nearer the door was a dozen workbenches arranged in
file. At these benches stood hardy women. As we walked towards them, I
could see their hands putting inserts into magazines like card sharps
playing Find the Lady.

One of the women smiled at us. Old Boy gave her a little wave.

`Look,' she called. `New blood!'

Old Boy clutched my shoulder. I patted his hand and tried to maintain a
reasonable distance from him.

`Don't worry about her, my handsome,' said another. She laughed, then
stopped abruptly. Her face was blank. `Worry about \emph{me}.'

Laughter spread throughout the room. I smiled and steered us both
towards what looked like a tennis umpire's chair near the loading door.
At its top was the factory supervisor, Madame. She looked unfriendly.

`Stop there,' she said, climbing down. Just as an ancient Chinese
mandarin would grow his nails to broadcast contempt for manual work, so
too did Madame. Such were their length that a Madagascan aye-aye would
have been happy to tap trees with them. She was very short. Looking up
at us, her nose wrinkled like that of someone forced to sniff sour milk.

`Now, are you pair going to be darlings or tinkers?'

I looked at Old Boy and wondered whether we should have arranged a `Make
for the hills!' signal. I could tell he was thinking the same.

`One of each?' I suggested.

For a moment, Madame's eyes threatened to turn us to stone, but then she
giggled. We braced ourselves. Her giggle became a wheeze that expelled
her smoky breath down to the last mouthful, until it became a series of
gasps that were progressively painful to hear. Turning blue, she waved
dismissively. `You keep up that sense of humour, my handsome. You'll
last longer. Got your G180s? Your GT4s?'

We gave her the paperwork.

`Right,' she said, `I suppose I should show 'ee around.'

We drifted into the files of workers. I felt like the president of a
banana republic inspecting his bananas. Most of the women were in their
fifties. They had tattooed eyebrows, sun-dried skin and piratical
smiles.

`They ain't much but you'll get used to their ways as the months go by,'
Madame croaked, her gaze raking the women with an intensity I usually
associated with small-arms fire.

`Months, eh?' I said, laughing loudly. `Will you excuse us for a
minute?'

I put my arm around Old Boy and steered him into the centre of the
aisle, where we could not be overheard.

`Now,' I whispered, `don't panic when I you ask this.'

`Ask me what?'

I looked both ways, then said, `Does anyone know we're here?'

`Right here? Nope.' He took out his phone. He swallowed. `No reception,
Andy.' He glanced at the fire exit. `No \emph{reception}.'

I let out a long sigh and thought about the summer, and my scattered
circle of friends from college. Nobody was doing this for the beer
money. We had to work. My textbooks wouldn't buy themselves. Pained, I
looked at Old Boy and gave him a Musketeer-calibre slap on the back.

Fact was, Old Boy needed this job. If he had to keep working at his
parents' bakery, with its night shifts and dark corners, he would lose
his last connection to the outside world and transform into some species
of serial killer who left a pasty next to his victims. I could see it
now; the \emph{St Austell Packet} would dub him the Night Crimper.

`Spin the dial on your chastity belt and set your charm to stun,' I
said. `We're staying.'

`One of them just licked her teeth at me.'

`Mate, just remember what's waiting for you at home. Pasty crimping and
days that start the night before.'

With the delicacy of a shark's head bursting through the bottom of a
pedalo, Madame stepped between us.

`Gad,' she said, `you en't got a pair of balls between 'ee, have 'ee?'

`I'm sure you're right,' I said, mindful of the reality of assisted
hara-kiri at her talons.

`Um,' added Old Boy.

`You see that grey door on the left?'

`We do.'

`Kitchen.'

`Understood.'

`You see that grey door on the right?'

`We do.'

`Shit house. Hope you enjoyed the tour, my lovelies. Now you,' she said,
pointing a stiletto-like finger at Old Boy, `set up here.' She rounded
on me. `But you, my lover, you'm going on the \emph{shrink wrap}.'

Around us, all conversation stopped. The noise dwindled to the extractor
fans, a radio advert for double-glazing, and the lonesome beep-beep of a
forklift truck somewhere. The ladies looked at me. Old Boy checked his
carotid pulse and counted silently. The malice in Madame's eyes--it
scampered from one orb to another, making her blink--suggested that I
should grasp her collar and wail, `Not the shrink wrap! Anything but the
shrink wrap!'

`Mm, OK,' I said.

Her expression soured. `Follow me.'

A worried Old Boy tapped his forehead in salute as I reversed away. I
returned the gesture and a lopsided smile.

Shrink wrap. How bad could it be?

But my cool thawed as we approached the thing. It was clearly an
infernal machine of the first water. It comprised an oven fed by a rough
conveyor. The oven rattled with a power I associated with
barely-contained rage. The lights of a dust-covered console gave some
insight, presumably, into the contraption's fell brain. These lights
were red and they were throbbing.

`Very nice,' I said. `What does it do?'

She cackled. `Yeah, you'll fit in alright.'

`No, seriously. What does it do?'

`Diddy Brooks,' she said wistfully, transported by a memory, `he used to
work on the shrink wrap. He had a sense of humour.'

`Don't tell me. He was shrunk and wrapped.'

Madame said nothing. Instead, with a smile, she slapped a red button in
the centre of the console. Then she walked away. The machine awoke,
accompanied by a sound that could only be described as a bus fart with
soot follow-through. The rear conveyor started, then the front conveyor.
A yellow light began to flash on top and a siren blasted wah, wah,
\emph{waaaaaah}. I covered my ears and ran in a very small circle a few
times. Then I detached at a tangent and hurried to Madame.

`But what am I meant to \emph{do}?'

`Gad.'

`I know. It's awful, isn't it? Training.'

She pointed at something near the mouth of the shrink wrap. `See that?'

`Yes, a pallet with magazines on top.'

She pointed near its arse. `See that?'

`An empty pallet.'

`Put the magazines through, one bundle at a time, and when they come
out, sling 'em onto the pallet.'

`So I need to move constantly from one end to another?'

`You got it.'

`Wouldn't it be more efficient,' I said, bracing myself, `to have one
person at each end?'

She fixed me with a frown that lasted long enough for me to think about
waving my fingers before her deadened eyes. Then she laughed and walked
back to the umpire's chair, mounting it with the uncanny fluency of a
chimp.

I watched her settle into the chair and click the safety belt.

Sighing, I set to work. The first order of business was to cut my palm
on the plastic strap that tied the magazine bundle. This done, I
wandered to the kitchen in search of a first-aid kit. Five minutes
later, I was on the shrink wrap, heaving bundles with the best of
them---that is, me. In an effort to pass the time, I worked like the
Devil Himself for a spell, then checked my watch. 11:05 am. I tried
working hammer and tongs. The watch read 11:08. I switched to working
like a man possessed. 11:09. I briefly flirted with working like it was
going out of fashion, and when I saw that my watch still read 11:09, I
put it next to my ear and shook it. Broken. Squashed between a magazine
bundle and the conveyor belt.

`Excuse me, do you know when lunch is?' I said to a short woman as she
dropped her bundle of magazines on the pile. In reply, she cracked her
knuckles.

`Well,' I said, `that's---'

`Oi!' screamed Madame, `you'm backed up.'

`Sorry?' I said.

`I'll give you ``sorry''.'

Without thinking, I snapped. `I'd rather just know what you're talking
about.'

Judging from her baby-in-a-high-chair wobble, she wanted to box my ears
for me, but the action would involve climbing down, walking, and so on
and so forth. Instead, she extended a hand towards the exit of the
shrink wrap. Her nail was almost long enough to tickle it. `You've been
loading up for half an hour---'

\emph{Blimey,} I thought, \emph{has it been only half an hour?}

`---and you haven't stacked the processed bundles on the pallet. That
forklift's waiting there to put the pallet on the lorry.'

I stepped away from the loader and looked around the machine. There was
indeed a forklift truck driver on the other side. The driver was dozing
on his steering wheel.

`Oh, yeah.'

`I'll give you ``Oh, yeah''.'

I walked to the rear of the shrink wrap. My magazine bundles had been
neatly covered in a cellophane-like plastic. I picked one up. It was
hot. A pair of gloves hit the side of my head. I thanked Madame and put
them on. They were large enough for an old-fashioned feather striptease.

`Any big Mickey Mouse ears to go with these?' I asked nobody.

I loaded the bundles onto the pallet with as little clumsiness as
possible, which was a great deal. Half an hour later, having noted with
increasing alarm the popping sounds coming from my lower back, the
pallet was full. `Well done, my lover,' called Madame. Her smile
switched off. `I want 'ee to do one pallet every twenty minutes.'

I leaned against the conveyor cowl and mopped my forehead with one of
the gloves. It knocked my glasses off and I crouched wearily, shaking
off a mitt, to put them back on. As I stood up, the forklift skidded to
a stop less than an inch from my nose. The loading prongs were knighting
my shoulders.

`Are you trying to bloody kill me?' I said.

`Ah, to be sure, I'm not so, no,' said someone who was clearly not
Irish. He murmured, `But I bet ye deserve it.'

I squinted. `Doogie?'

`Ah, you're wrong there, so you are. Oi'm Wade.'

`No. You're Doogie Lobb and that's the worst Irish accent I've ever
heard.'

`Oi'm Wade, so I am.'

`You're Doogie, so you aren't.'

He tapped his identification badge. `Wade Rabey.'

`Wade Rabey? I think you're confusing yourself with your step-dad.'

`Wade. Rabey. If you get my drift, so you do.'

`Why are you winking, Doogie?'

Madame piped up: `What're you pair chitterin' about?'

Doogie fumbled with the controls and reversed the forklift into a
stanchion. Something plastic broke on the back of the vehicle and its
prongs wobbled.

`Christ,' Madame continued, `you'll scat the place down if you don't
look out.'

I put my glasses on and watched my best friend, Doogie, make sudden
turns, slide, teeter on two wheels, and generally avoid going anywhere
near his intended pallet despite cavalry-charge arm gestures in its
direction.

I could not fathom what he was doing driving the forklift. The previous
night, over a pint of the Speckled Dreckley, the three of us--Old Boy
included--had been talking about the job openings here at Smart
Publishing. Chiefly, this involved Doogie winding up Old Boy with
stories of workers crushed beneath rolls of paper, and bleaching
chemicals that turned your eyeballs totally white if inhaled.

To my knowledge, Doogie was still teaching kite surfing on Fistral
Beach, which he had been doing for the past month. It had followed a
stint as a burger van man (he was fired for falling asleep), a classroom
helper at Penrice Comprehensive (he spelled `lunch' as `l-u-n-t-c-h';
was fired), and a---brace yourself---skiing instructor. He wasn't
teaching that in Cornwall, of course. No, that would be the height of
absurdity. He was teaching it in Devon.

And was fired: A woman had slowed herself using the inside of her bottom
lip as a brake; lawyers were mentioned; Doogie fled for the Tamar in his
passion wagon, more of which later.

These thoughts passed through my mind as I watched Doogie pierce some
magazines with the forklift's prongs. By now, Madame had had enough of
this jiggery and decided that pokery was required. She climbed down her
chair ladder and secured Doogie's attention by throwing a roll of
masking tape in his general direction, then drawing a finger across her
throat. This was either a command to cut the forklift's engine or a
demonstration of what she'd like to do to the driver. Either way, he
stopped the forklift. Madame gripped the roll cage.

`Can't you drive that thing?' she said.

`To be sure I can, lass.'

`Oh, please,' I said, glancing upwards.

`Shut it, you,' he said.

Doogie glared at me, and Madame caught the exchange. `Do 'ee know each
other, then, or what?'

`Or what,' I said.

`What?'

`We don't know each other,' I said.

Doogie and I looked at one another. Over his shoulder, I could see that
the women had downed tools. Faintly, below the ambient mechanical
noises, the radio was playing Take That's \emph{Relight My Fire}.

Madame wrinkled her nose like a POW guard sniffing for sign of disturbed
earth. `You two look like you're up to something.'

`It's nothing,' I said.

`To be sure,' agreed Doogie. He forced a grin. `And aren't you a bonny
wee lass?'

`Shut your wap,' said Madame. Her eyes were stony. `Where did 'ee learn
to drive like that?'

`Ah, it's all the rage back in Oirland. Artistic flair, so it is.'

`Let me see your ID.'

Doogie passed her his stepfather's card. Madame squinted at it. `Wait a
minute. It says 'ere you'm forty-four years old.'

`To be---yes, I am. But I don't look a day over seventeen, do I so?'

`No, you don't,' she said coldly.

`'Tis me mother's complexion, so it is. Ah, and the spring waters of the
Mullish Kintyre.'

She tilted her head. `Don't 'ee mean the Mull of Kintyre? In Scotland?'

I folded my arms, then put my hands over my face. Doogie cracked on. He
was committed. `To be sure, there are many Mulls, and several Kintyres,
but only one I call home.'

`Which one?'

He thought for a moment. `Home.'

I peeked through my fingers at Madame. She was frowning at the ID badge
but a fast look at the idle women suggested she wanted the situation to
resolve itself one way or the other.

`Alright,' she said, with a sigh. She tossed the ID back. `But I don't
want to see any more artistic flair.' She rounded on me like the
slightly-more-disturbed grandmother of Edward Scissorhands. `And that
goes for you, too.'

She tottered slowly back to her umpire's chair. When she had reached the
top and settled in (click of seatbelt), I stage-whispered to Doogie,
`What the hell are you playing at?'

`I suppose,' he said, dropping the Irish lilt, `butter wouldn't melt in
your mouth. To think, I'm in desperate need of a job and I find out you
and Old Boy have filled the vacant positions.'

`What? We told you last night we were coming here.'

`You told me you were going for an interview. I never thought for one
second they'd employ Old Boy. Besides, I didn't need a job then.'

I put my head into the roll cage.

`You were fired between ten o'clock last night and this morning?'

Doogie looked indignant. `Someone told them I'd borrowed a parachute to
go camping with Alice Walters, next week.'

`A parachute?' I said. 'What's that got to do with camping?'

`Do you know how much a tent costs?'

`You eejit. What's your step-dad going to say when he finds out you've
stolen his forklift certificate?'

`He's never going to find out. He'll be happy enough when he gets his
rent cheque.'

`Which he'll then need to use for your bail, probably.'

A box of Tic Tacs struck me behind the left ear.

`Oi, you pair,' shouted Madame. `Get a shift on. I won't tell 'ee again.
Wade, you get the pallet away before I come down there and box your ears
for 'ee. Andy, you get sticking they magazines through. If we don't have
this order out by five o'clock, there'll be heng to pay. Look at that
bleddy backlog.' She blinked thoughtfully. `Gad, you'll need some help,
I suppose. Someone with a bit of masculine grunt about them.' (At this,
Old Boy closed his magazine triumphantly and began to walk towards me.)
Madame continued, `But Sarah en't working today, so that bandy-ass mate
of yours will have to do.' (Old Boy paused, then resumed his walk,
shoulders hanging lower than before.)

`Hello, Doogie,' Old Boy said, `what are you doing in a forklift?'

`Oi'm Wade, you Sassonack. Speak to your wee friend if you don't believe
me.'

To emphasise his point, Doogie reversed away into a skid, then gunned
the forklift towards us. I hustled Old Boy behind me just as the
forklift braked and slid its two prongs into the base of the palette.

`There,' said Doogie. He sounded surprised. `Easy.'

When we were safely on the other side of the shrink wrap, Old Boy looked
around.

`What do we do, Andy?' he asked.

`See those magazines?'

`Yeah.'

I mimicked Madame's Cornish accent: `Sling 'em on this 'ere conveyor.'

`That doesn't sound too bad.'

`My friend,' I said, `this is the shrink wrap. Be afraid. Be very
afraid.'

`I've got paper cuts on my paper cuts. And I was sexually harassed. I
actually prefer it over here.'

`Come on, then, muscles.' Cornish accent again: `Let's get a shift on.'

I grabbed a bundle near Old Boy and threw it onto the shrink wrap. In an
unexpected move, he dived after it and sprawled across the conveyor. He
drifted away, looking at me as though I were insane.

`Well,' I said, `how does that help?'

With rapid, bird-like movements, he switched his attention from me to
the magazines. He tugged at his trapped right hand. `Thumb's caught.'

I tried not to look perplexed. `Your thumb's caught?'

Old Boy flushed. `That was my bundle. I was preparing to ``sling'' it.'

I flapped my arms against my thighs in exasperation.

`You should have bagsy'd it. You know, got dibs on it.'

Old Boy looked up the conveyor. He was still attached to the bundle.
`I'm going to die horribly.'

His nervous ear was twitching.

\chapter{}

\lettrine{T}{ he} shrink wrap worked by passing bundles of magazines between two rolls
of transparent film. Once mummified, the material was cut by a
guillotine to form a separate sack of film for each bundle. On the
bundle would go, through the large, central chamber of the machine where
a blast of heat would shrink the plastic.

Old Boy was less than a metre away from the film rollers when he braced
his feet against the metal arch that held them. The conveyor belt
continued to move beneath him, tugging at his shirt.

`Andy!' he screamed.

Waist-high safety baffles stopped me from getting closer. If I were to
help, I would need to climb onto the conveyor belt too. Meanwhile, Old
Boy's cheap, gripless school shoes began to lose purchase against the
metal frame. In front of him, downstream, the film guillotine shooshed
up and down, leaving flat clear bags to shrivel in the heat of the
machine.

`What are 'ee bleddy doing?' screamed Madame. I turned to see her
highchair rocking with panic. `Get your Cornish ass round that bleddy
machine and turn it off 'fore I come down there'n sling you through it
too.'

I took what was, in retrospect, the scenic route: I leapt across a sack
trolley, caught my toe in it, and bounced my head off the heating
chamber. While I recovered my composure and studied the control panel, I
heard Doogie's forklift skid to a stop behind me. I turned to see him
leap off it with a swashbuckling, `Y'hah!'

`What is Old Boy playing at?' he asked.

I waved for silence and tried to focus on the control panel. `Cleaning
the conveyor belt with his arse, what do you think he's doing? Go and
pull him off while I figure this thing out.'

`Leave him to me,' he said, leaping away. I wished he would stop keeping
his head while I was losing mine. It was difficult to concentrate.

Madame screamed again, `The red button, you daft dapeth!'

`There are no red buttons.'

`It's looking right at you.'

`There's a blue one,' I said, frowning.

`Push the red one, shit bag.'

I whirled around and flapped my ridiculous mittens as though inviting an
aeroplane to land. `There is no red button.'

Madame's gorgon eyes blazed.

`Alright,' I said. `I'll check again. Ah, now. There is a crimson one.
Though ``carmine'' would be a better term.'

`I'll frickin' swing for 'ee.'

I slapped the crimson button, investing all the strength at my call. The
button broke with a dull `boing' sound and fell onto my left shoe, where
I stared at it.

`He's broken the fail safe,' said Madame. Her voice had softened with
disbelief. I could hear the murmurs of the women passing the news
around. `He's broken the fail safe.'

The conveyor belt made a sound like slipping gears. I turned to see that
Doogie was on it now, adding his weight and resistance as he reached
forward to grasp Old Boy. Doogie snagged his collar with his left
hand---throttling him---and held on further back with his right. He
looked like a man interrupted mid-buck on a bronco.

`No,' croaked Old Boy, `air.'

His quivering legs folded like windscreen wipers in a car crusher. He,
and an off-balanced Doogie, collapsed. They were taken towards the film
roller, where both were neatly swathed.

\emph{So far so survivable,} I thought.

Then they moved into the slamming jaw of the guillotine, which was
striking the conveyor with regular, satisfying thumps. As it slid up for
its next chop, Old Boy, foetal and gibbering, passed into its maw. His
eyes widened with terror as it rose up---

\emph{Shoosh.}

---And down.

\emph{Shoo-bft!}

For a scrotum-tightening moment, I thought the blade had shortened my
friend by a few inches, but as he passed on I could see that he was
whole.

Doogie, by contrast, was not going to be as lucky. The blade rose again.

I flopped over the guard shield and crawled down the conveyor. With the
guillotine a split-second from its cut, I took a handful of Doogie's
hair---though, truth be told, his collar was equally convenient---and
yanked him.

`To me!' I shouted.

\emph{Shoosh.}

From my perspective looking down his body, the guillotine passed through
his feet, but as the blade lifted up it was clear that Doogie had not
been touched. He batted at my hand, but this only lengthened his body
and put his head in danger of the next chop. I had no choice; I had to
put my foot on his head and push. Well, in the technical sense, I did
have a choice. I could have pushed him with my hand. But that's one for
the lawyers.

\emph{Shoo-bft!}

The guillotine dropped once more and brushed the crown of Doogie's head.
I let out my breath. I watched Doogie pass, after Old Boy, into the
oven.

I tried to look on the bright side. In one sense, my plan had been
successful. In another sense---the sense associated with, say, a
guillotine striking my foot in a sudden blaze of pain---

\emph{Shoo-bft!}

---the plan was suddenly, heart-stutteringly unsuccessful. I leaned back
and howled at the asbestos ceiling tiles. The watching factory workers
sang, `Oooooh,' as though I were a tennis player sliding into the
splits. The pain was like a loud noise, even deafening, but I had enough
awareness to curl up and put my fists against my head. The blade came
down again and missed me.

Through my frosted plastic shroud, I saw people running towards the
shrink wrap. The throb washed up my leg as though I had collapsed at the
very shore of oblivion. I struggled to keep my thoughts on positive
lines as the conveyor belt bore me solemnly onwards into the oven that
would blast me with hot air before spitting me into the bin of magazines
and two familiar, flambéed companions.

I heard the roaring of fans. The light of the world went out. I dared
not breathe. Back to me flew all the memories of the ghost trains I had
ridden as a child: here a skeleton painted with uneven fluorescent
paint, grinning and waving pip-pip to the tune of a tired motor; there a
bat bouncing on elastic. I recalled dirty vampires flashing and the hiss
of dry-ice.

Then daylight. I felt cold rollers beneath my back. My mouth had been
sealed with hot film. It clung to my whole body like an immobilizing
skin. I was trapped in my sideways crouch and could do nothing as I slid
down the slipway and bounced into another body. The pain in my foot
restarted.

A nail slipped across my face once, twice, snicker-snack. As it passed
my mouth, I gasped and took swallows of air. Everything sounded hollow.
The plastic had sealed my ears. I turned to see Doogie was next me. A
strip of film had stuck to his beard, shutting his mouth. Old Boy, also
alive, fingered the film over his closed eyes with a free hand.

Though the world was muffled, I could hear an alarm. A red light was
pulsing too. It reflected in the greasy foreheads of the factory ladies,
who had formed a crowd around the shrink wrap. I felt like an astronaut
at a press conference. I managed to tear the film around my right hand
and, this done, I popped a hole in the plastic over my ear.

Madame had the exhausted, numb look of a person who had risen to anger
so quickly she had smashed through the glass ceiling of fury and been
knocked senseless in the process.

`Never,' she gasped, `never in my born days.'

`We're alive!' I said. `Knew we'd be OK. The thermal properties of
polyolefin mean it doesn't need that much heat, interestingly.'

`Mmmm,' said Doogie.

`Hello?' asked Old Boy.

`All that palaver, eh?' I said. `We must have given you quite a stir.
Anyway, back to work we go.'

`You hold on there, my lover. You've got some explaining to do. Mr
Smart?'

Abruptly---because I hadn't heard his running footsteps---Mr Smart
appeared. He was out of breath and his damp shirt was stuck to an
unnaturally chiselled physique.

`Someone tell me why I've been interrupted from Harry Secombe's final
album \emph{I Did It: Highway}.'

`Look at 'em,' said Madame, pushing her chest out. For a moment, I
thought she would cite her breasts as the cause of the emergency, but
then she gestured towards us like a weather forecaster directing the
viewers' fancy to a storm front.

`Dear God, have you been through the shrink wrap?'

\emph{Count to five,} thought my brain. \emph{Do not ask him what
brought him to that conclusion.}

Slowly, I said, `We have quite literally been through the shrink wrap.'

Mr Smart looked from me to Madame and back again. My ankle throbbed. She
shrugged. I tried to shrug too, but the wrapping was too tight.

`They en't got an ounce of common sense between 'em.'

`Well,' I said, `you didn't show me how to use the machine properly.'

If a movie were ever made of my life, I looked forward to consulting
with Jim Henson's Creature Shop on capturing the arachnid movements of
Madame.

`You liar,' she said, turning to Mr Smart. `I did tell him.'

`When I asked her for health and safety advice,' said Old Boy, `she told
me to stay safe and healthy.'

`Is this true, Yvonne?' asked Mr Smart.

`Liar,' she said. She poked my chest once. `He climbed on the bleddy
machine. Didn't he, girls?'

There was a grumble of agreement.

`Oh yeah, he did.'

`I seen 'im.'

`Up on the machine, straight up. I never seen nothing like it. Have you,
Polly?'

`I like that little tacker. The one who went through first.`

Old Boy's hands scrambled around him as though feeling for an ejector
seat release.

I struggled again at the film, but I could not rescue myself from
confinement any more than I could shake the impression that I was a
raving loony in a straitjacket protesting his sanity to a kindly
psychiatrist who would be only too happy to relieve me of my prefrontal
cortex if I didn't stop gibbering.

`Look,' I said, `what happened was this. I tried to turn the machine off
when I saw Old Boy was on the conveyor belt---'

`Hang about,' said Mr Smart. `Why was your friend on the conveyor belt?'

`Um,' said Old Boy.

`Well,' I said. `That's because I---'

`I tripped! My fault!'

`You tripped over the guard shields?' asked Mr Smart. His forehead was
unhealthily corrugated. I could tell we were not winning him over.

`Right!' said Old Boy.

`You're fired,' said Mr Smart.

`Right!'

`Now you,' he said to me. `Why didn't you stop the machine?'

`There was a problem with the knob.'

`Are you trying to be funny?'

`Actually, I was too busy directing aircraft with these gloves.'

We looked at one another for a considerable time. `Now I'm trying to be
funny,' I said weakly.

`Try this: you're fired.'

`Ah.'

`And you,' he said, taking a firm grip of the film gag across Doogie's
mouth. `What have you got to say for yourself?' He swept the gag from
Doogie's face.

`Jaysus!'

The film carried a Turin Shroud of Doogie's adolescent beard. Mr Smart
tapped the ID on my friend's lapel. `Wade---You're the same Wade who put
the prongs of his forklift through the fence this morning.'

`Conditions were\ldots{}were\ldots{}' Doogie looked at me desperately.

I panicked. I said, `Icy.'

Doogie looked like a deep-sea submersible pilot whose companion has just
confessed to an explosive gastric ailment.

`Yeah,' he said, more to me than Mr Smart. `It's been a particularly icy
summer.'

I looked at my shoe. The heel had been split in two by the guillotine.

`I sent you up here to stay out of harm's way,' continued Mr Smart. `Not
one of my better decisions.' He squinted at the ID. `Are you really
forty-four years old?'

`If I look younger, it's because I've kissed the Blarney Stone, so I
have.'

`Well, you're fired, whoever you are, and be grateful I don't take legal
action,' said Mr Smart. `Once you've been cut free, get your stuff and
get out. Andy, I'm particularly disappointed in you. As for this one, I
remain unsurprised.'

`But,' said Old Boy.

Mr Smart stepped back and nodded to Madame. She sneered as she
approached, her nails clicking like black mandibles.

\section*{}

We were without a car between us, so we walked up the hill from the
industrial estate to the town centre. It passed noon. The air wobbled
with heat and the traffic on the road to Par was slow and heavy. The
flowers of the Penrice roundabout had been arranged in beds by colour
and they blazed red, yellow, and blue. An ambulance overtook a lorry. It
brushed against the curb and sent up a bank of dust, which we trudged
through.

`If your thumb was caught,' Doogie said for the twentieth time, `why did
you have to jump after it? Why not just stand where you were and move
your arm?'

Old Boy just kept walking.

`Doogie,' I said, `these points would be more devastating if you had a
complete beard.'

`I know that.'

When we reached the high street, I drew out some cash using my credit
card and treated everyone to pasties. We ate them leaning against the
guardrail on the top level of the multi-storey car park.

Doogie sighed. `Sorry, mate.'

`That's OK,' Old Boy said.

They clinked their bottles of Panda Coke. Afterwards, we balled up the
greasy wrappings and played football until Old Boy twisted his ankle on
a lolly stick. We had enough change to play pool in an arcade near the
Priory Car Park, so we did that. The crowd was a mixture of college
friends and mates from school who, in the interval since I last saw
them, now looked alarmingly grown-up; the old friendships and rivalries
were crumbling away as we left childhood behind. Things that had seemed
so important at school---where you sat, who you talked to, what you wore
on non-uniform days---now seemed trivial. While chalking my cue, I spoke
to Del Cundy for the first time since he'd ripped open my armbands with
his teeth during a swimming lesson in the first year at St Mewan. He had
mellowed.

Around teatime, Old Boy told us he had to go home. He had a curfew
because his parents went to bed early. Doogie and I finished our game,
scooped the remainder of our twenty pence pieces from the side of the
table and nodded our good-byes to the crowd. The clientele was changing
into a different sort altogether, anyway. These older, more leathery
types were in the foothills of a night on the razz.

Outside, it was still hot.

On a typical evening, Doogie would have driven us home in his Ford
Escort, The Chariot of Phwoar. But its battery had been dead for a
fortnight, so I sat with Doogie in the Trinity Street bus shelter as we
waited for the 522. We spoke about our plan to teach English in Japan
and learn karate from the supernaturally gifted masters there. The
conversation was a stale one. We both knew it wasn't going to happen.
When we were fourteen, our dream had been a computer shop. When we were
ten, it had been jobs at the North Pole as elves.

`Andy,' Doogie said, in a tone that suggested he wanted to close the
book forever on Japan, `Wade wants to kick me out.'

A couple of years back, Doogie's life had worsened with the arrival of a
lodger called Wade, who had a penchant for convoluted Jethro jokes and,
it turned out, Doogie's mother. Doogie now had a young half-sister by
Wade and found himself being eyed up during teatime discussions about
the weight of the family airship, so to speak. Wade had increased
Doogie's rent in line with inflation. In Argentina.

A half-size bus rounded the corner. Its destination read, `St Dennis'.

`That's me,' said Doogie. `See you tomorrow.'

`Wait, what's tomorrow? Sunday? Is it that thing?'

`Yes, it's that thing,' he said, speaking clearly as though to an
elderly relative. `Don't forget your contact lenses, or you'll be no
good to anyone.'

There was an old lady getting off the bus. Doogie took her wheelie
trolley and placed it on the pavement. Then he flashed his pass at the
driver.

I looked at my watch. There was a programme on Radio Four about dark
matter and I was probably going to make it.

`And wear a thick jumper,' said Doogie, his mouth at an open window,
`even if it's hot. You won't bruise as much.'

`We're bringing Old Boy, right?'

Doogie gave me a crooked smile.

\chapter{}

\lettrine{T}{ here} are parts of St Austell, mainly to the north, that look like the
moon. Centuries ago, someone dug up kaolin---china clay---and, knowing
it would make paper shiny and pills easier to swallow, dug up some more
and kept on digging, covering the countryside in white craters. In the
late eighties, my father had apprenticed for the company that mined the
clay. He used to come home with white dust covering his metal-capped
boots.

Thirty thousand people lived in St Austell in 1999, the brink of the
twenty-first century. Our town is to Cornwall as Birmingham is to
England. Winters are damp. It never snows, no matter how hard you
concentrate. You can run through the ruined landscape of clay tips and
throw clay balls if you want---but you won't. In summer, when the air
wobbles with heat and the roundabouts fill with flowers, the whole world
comes to Cornwall.

Here is a new Mercedes with a Bailey caravan, top of the range. Here are
children called Chloë and Simon. Chloë has a net for the rock pools.
Simon has plastic dinosaurs to guard his sand castles. Here are BT
operators on a hen weekend. Doctor Thompson, retired, on his Harley
Davison. The Makepeace family are driving to their second home in
Padstow.

These tourists move like a wave of buffalo. The natives waylay them with
trinkets, housing, scenery, best bitters and occasionally give them
directions that lead them off cliffs. Relatively few tourists stop in St
Austell, where granite has rotted to form china clay, and fathers stamp
the white dust off their boots before coming into the house at tea time.

There is a woodland near my house---I can see it from my bedroom
window---where no tourists go. It is Luxulyan Valley. Doogie, Old Boy
and I are driving there now in the resurrected Chariot of Phwoar.

\section*{}

It was our Arts and Crafts teacher, Mr Jones, who pronounced the
`Poverty in Cornwall' painting created by Doogie and me `pretty
contemptible' because some of the homeless looked like our classmates.
Henceforth, the pair of us, and whoever else we deemed worthy of
inclusion, were known as the Young Contemptibles. We had kept the
nickname throughout our school life, and it was this group identifier
that Doogie had provided on the insurance forms for the paintball
company, Stingers.

Old Boy, a late addition, had never been a Young Contemptible. I gave
him the accolade as we were wheel-spinning away from his parents'
bakery, partly in recompense for our sudden appearance in his life that
morning.

`Think of this less as a kidnapping and more as a field promotion,' I
said. `Welcome to the club.'

Old Boy probably thanked me at this point. It was difficult to hear him
over the theme from the film \emph{Bullitt}, which Doogie played, at
some volume, when he needed to drive fast. Plus I was holding Old Boy in
a companionable headlock.

As we dropped down into Luxulyan Woods, the sunlight faltered before
failing entirely at the pit of the valley. Branches were low enough to
brush the car. The road surface changed from cracked tarmac to pot-holed
tarmac, to no tarmac at all. We splashed through a high ford, and when
Doogie wiped away the muck from the windscreen, we saw the sign for
Stingers.

`What's that, mate?' I said to Old Boy. I could feel his jaw moving
through my arm.

`I said, ``Why do you need me?''\,'

`It's the latest stage in my programme to get you out of the house
more.'

`Plus,' called Doogie, swinging The Chariot of Phwoar through the gate,
`the Trethewey brothers got the shits.'

\section*{}

Thing was, Doogie and I liked to drink at the White Gold---the Goldie,
to its friends---over near the Mevagissey Roundabout. The pub used to be
a mill on the White River and there is still part of the huge wheel axle
in the games room. It's not too popular with students because of its
reputation for violence. This reputation is, of course, somewhat
exaggerated for effect, though I have heard of a local biker gang
setting about the St Austell College bridge club with Super Soakers one
summer afternoon. This reputation meant that you could actually get a
seat in the evening, which marked it out as an oasis in the desert of
rammed pubs around the area.

One of the regulars was a tall, broad-in-the-beam character called Big
Jeff---though not to his face. He wore leather boots with hobnails, a
belt like a weightlifter's, and a Russian army coat. He was reliably
grumpy unless he was making fun of one of the uneasy, deferential crowd
who hung around him at the bar. Big Jeff was the owner of Brown's
Ice-Cream. You've probably heard of it. If you've been to Cornwall and
ordered a frozen treat from a van on a beach, the chances are that
Brown's Ice-Cream made that whippy, choc-ice or lolly. Nobody used the
word `mafia', but it was obvious that Big Jeff had connections of the
'bada-bing, bada-boom' variety.

Doogie tended to order drinks because he had a Cornish accent, or enough
of one to escape notice. I, on the other hand, sounded like a Radio Four
continuity announcer in tight trousers. Unspeakably non-local, and
asking for a slap. Doogie and I would tiptoe past Big Jeff on the way to
the rickety conservatory that appended the games room. Once there, we
would drink in splendid isolation. At least, that was the usual routine.

On this evening---it was the Wednesday prior to the paintball---we never
made it to the games room.

First, I noticed a woman in the group around Big Jeff, listening to one
of his stories. There was nothing flashy about her clothes. She wore a
checked blouse, jeans and white trainers. These clothes---peripheral
irrelevancies---were enough to make the edge of my vision crinkle with
starlight before I even considered the body underneath. In fact, the
non-flashiness only underscored the effect of her eyes. They were
moonlit. Perfect. She was looking across the room as Doogie and I
entered. Her bored glance crossed me, hesitated, and came back.

She smiled.

At me.

`I'll get them in,' said Doogie. `The usual?'

The majority of my brain was occupied in figuring out whether this
beautiful girl was truly looking at me or, more feasibly, the slightly
better looking Doogie. I was working in Shoe World at the time, and the
first rule of shoe retail came back to me: don't expect an old boot to
sell if you display it next to a snazzy trainer with those little
air-pump thingies.

Doogie took a position at the bar next to Big Jeff. The girl's moonlit
eyes had not followed him. She was still smiling at me. Encouraged and
baffled, I moved towards her through the regulars. There was a piece of
mill machinery above the bar---something like a plough---and its end
pointed down at her. Big Jeff had his back to us. He was laughing. It
sounded like a man banging to be let out of a wardrobe.

She had scarlet stripes in her brown hair. Her eyes were steady and
confident. As I stopped, a little too far away to be normal---a great
start---she rolled her eyes in mock boredom and tipped her head at Big
Jeff. Being a male of the species, I began the usual business of
collecting and sifting every element of her smile for the gold of
genuine attraction and the possibility that she might, one day, given
the right circumstances---and, if necessary, alcoholic beverages---agree
to have proper sex with me.

Proper sex, mind. With the lights on.

Ironic, then, that I chose to destroy the possibility of such a scenario
by holding out my hand and saying, `H'mah!' which isn't even a word.

`Andy,' she said. `Hello.'

\emph{She knows my name,} I thought.

Panic.

Had she been in the year below mine at school? Had she borne witness to
the horror of my reading of the Twenty-Third Psalm when, before a packed
assembly hall, I had actually vomited with nerves into The Good Book,
closed it, and passed it to the horrified Mr Goudge standing behind me?

I decided to shake her hand.

`Hello.'

`Not many people our age do this,' she said. `Shaking hands, that is.'

\emph{Andy, this is your brain speaking. You've been shaking her hand
for some time. Best to stop. Otherwise she'll think you can't even
handle the most basic of social situations.}

I swallowed dryly.

\emph{But it would be awful, wouldn't it?} continued my brain. \emph{If
you could think of nothing to say.}

\emph{You know: Nothing.}

\emph{At.}

\emph{All.}

My belly swirled with acid and bile. Adrenaline washed through my limbs
and lit fireworks in the middle of my---already tired and
emotional---brain.

`Um,' I said.

Her smile froze and I could feel her prepare for the conversational mode
that permits a person to interact with a two-year-old who keeps handing
you teaspoons and singing a nursery rhyme in response to questions about
his snappy new jumpsuit.

`Well,' she said, `of course, it's nice to meet you again.' She reached
across with her left hand and rescued her right from my sweaty mitt. She
pursed her lips and nodded.

\emph{She knows me. How?}

I raised my eyebrow and circled my head in a manner designed to both
acknowledge that I recognised her and to suggest that she give me more
details.

\emph{Oh, look, Andy. Another period of silence is starting.}

`So,' she said, `how have you been?'

\emph{Deep breaths. Articulate yourself.}

`Fine,' I said, `I've been fine. You look nice---today.'

\emph{A masterstroke. Now ask her if she'd like to see some puppies.}

`Thanks,' she said. She lifted a spirit glass to her lips and took a
sip. She was on the brink of another smile.

\emph{Right, forget the puppies. She thinks you're being ironic. She is
impressed by your post-modern approach to conversation.}

`I---I---'

\emph{Oh, for the love of, and so on.}

`Yes?' she asked.

`You look nice today.'

\emph{Andy, remember this moment for every day that remains of your
sexless life.}

In the midst of this little death---as sweat ran down my forehead,
collected on my eyebrows, surged from my armpits and babbled down my
back---I whispered, `Try to stay calm, idiot.'

`I'm sorry?'

\emph{In another brilliant move,} thought my brain, \emph{you've managed
to say that out loud. If it's alright with you, I'd like to transfer to
another body. I don't like the mouth on this one.}

I'd solved time dilation equations with less effort than it took to
compute this conversation. I should note that, as a card-carrying
physics geek, stereotypes dictate that I should be unable to start a
conversation with a woman unless our hands touch by accident in the
salted snack bowl during Spock's death scene at the end of \emph{Star
Trek II: The Wrath of Khan}. But I can hold my own, even against the
sporty Doogie, provided we're at a nightclub and I remove my glasses.
Deafened, partially blind in a darkened environment, and quite drunk,
things often proceed swimmingly.

Sober, however, sweat equals mass multiplied by the square of panic.

`I'm starting to think you don't remember me,' she said.

I had never spent so much time looking at a pretty, amused face. A tear
of sweat broke from the cover of my hairline. I began to think about
wiping it away, then began to think about thinking about wiping it away,
then I stopped thinking.

She laughed. Her eyes---which, unlike mine, she was fully in control
of---crinkled wonderfully.

`I'll give you a clue: electricity.'

`You don't work in Curry's, do you?'

I allowed myself a closer look at her face. She lost a fraction of her
composure under my stare, but not the slightest recall stirred in my
memory.

Meanwhile, she was looking at me as though I were insane.

`Here,' said Doogie, passing me a pint, which slipped through my
fingers, struck my foot, and sloshed to an unfeasible height up Big
Jeff's back.

I stood there for a long time. My hand remained in a pincer-like
configuration. We all stared at that hand. Doogie stared at it; the
unknown woman stared at it; and Big Jeff, revolving slowly like Bully's
Special Prize Board, stared at it. Soon everyone in the pub was staring.
Conversation dwindled. For the first time, I could hear the juke box. It
was playing `Rabbit' by Chas and Dave.

The beer had splashed right up to an epaulette on Big Jeff's coat. He
swayed like a bear shot by an insufficiently powerful tranquilliser
dart. His face went through a series of expressions: from surprise, to
intrigue, to anger.

\emph{`--Rabbit-rabbit-rabbit-rabbit--'}

`What the bleddy hell do you think you're playing at?'

Beer dripped.

I looked at my hand. I had no idea how to explain that I had
accidentally dropped my pint.

`I dropped it,' I said.

Big Jeff gurned.

`I can see that, shit-for-brains.'

`Accidentally,' I added.

My hand was still in the pincer position.

Big Jeff gathered the fabric of my shirt in one, large paw. I felt a
button pop.

After that, all the stopped up energy in the pub seemed to release.
Everyone came to life. I remember the woman holding on to Big Jeff's arm
and telling me it would be better if I left. At the same time, Doogie
laughed politely, unhooked Jeff's hand, and led me through the surly
onlookers to the door of the pub.

\emph{`Rabbit-rabbit-yap-yap.'}

We took a shortcut home through some gardens. I kept telling Doogie
about the woman and he kept telling me to shut up.

\section*{}

Above Luxulyan woods, clouds had gathered. The paintball marshal left us
with a laminated set of instructions for the forthcoming battle. The
rules, I explained to Old Boy as he looked at his equipment with growing
incomprehension, could be summarised as: shoot the other guys as much as
possible and your own team not so much.

We sat on the bank of a stream. I had laid out my weapons: a paintball
gun, hopper empty; waterproof trousers and coat, green; Hannibal Lecter
mask, visor attached. Old Boy had done the same. But our piles amounted
to less than half Doogie's paraphernalia. He had a bandolier, spare
hoppers, kevlar gloves, some kind of stock extension, and grenades. The
grenades, he claimed, were perfectly safe---not much more powerful than
a shaken fizzy drink bottle.

Doogie spread an icing of mud across his forehead, cheeks, and what was
left of his goatee.

Old Boy turned to me. `Do we have to do that?'

`Mate, nobody has to do that.'

Doogie's hair was covered by the hood of his waterproof coat and his
eyes were protected by a visor so thick it would be perfectly safe,
medically speaking, for him to do some spot welding as we waited for the
game to begin. He had scrawled `Born To Kill' across the top in white
correcting fluid. On my own visor, at Doogie's urging, I had written
`Animal Mother', but my writing was so neat that the effect was ruined.

Doogie hefted his gun. He rested the barrel in the notch of his elbow
and practised shooting at the trees, which he had labelled, with no
detectable irony, `native insurgents'. Next, satisfied that he had
taught some foliage a lesson it would not soon forget, he tested the
tightness of his outfit with a slow dance that looked like a dizzy T'ai
Chi master feeling for a light cord in a darkened bathroom.

Old Boy still wore his white overalls. There were traces of chocolate
milkshake either side of his mouth. He gave his hopper a tentative
squeeze. He looked like a kidnapped surgeon poised to operate on a
dictator.

`Mate,' I said, `have you ever played paintball?'

`No. But I did see \emph{Apocalypse Now} the other night.'

`All you have to remember are two things. If you see someone wearing a
yellow armband, shoot. If they're wearing a blue armband, hold your
fire.'

Old Boy raised his eyebrows. Which is to say, he moved his brow ridges.
His eyebrows remained motionless on some shrink film a few miles away.

`Is it that simple?'

`Absolutely.'

I unfastened the hopper on my gun and dribbled some blue paint balls
inside. The visor looked a little too small to accommodate my glasses. I
took them off and put them in the map pocket of my trousers.

`Hey, Andy.' Doogie offered me a tube of something. His expression was
that of a person about to magnanimously turn down heartfelt thanks.
`Mozzie rep?'

`Mosquitoes? In Cornwall? Good thinking, private.' I threw the mozzie
rep into the bushes and said to Old Boy, `Doogie has left the building.'

Old Boy sniggered, which sounded like someone stifling a number of
sneezes: `\emph{Gh'k. Gh'k. Gh'k.}'

`Nice,' said Doogie, aiming for the tone of a person who could produce a
withering reply if necessary but would not, on this occasion, bother.
Just then, there was a burst of static from his walkie-talkie. He
plucked it from his lapel and treated the Luxulyan woods to a
thousand-yard stare. `Broadsword, this is Danny Boy.' Unintelligible
crackle from the radio. `Roger, we are ready, over.'

Doogie presented me with a closed fist, which he then opened.

I sighed. This was one of the commando signals he had asked me to
memorize on the way over. Rather than risk the intricacies of another
lesson, I did the same gesture back.

Doogie looked at me as though I were a fool.

`Synchronise watches, gentlemen,' he growled. `It is 0930---now.' He
shut the flip lid on his wristwatch and began tightening various Velcro
strips about his person. When he noticed Old Boy and I had not moved, he
said, `Why aren't you synchronising?'

`I don't have a watch,' I said.

`Mine thinks I live in Venezuela,' said Old Boy.

Doogie sighed. `Just lock and load, people. Check your weapons and your
webbing. The Young Contemptibles are moving on up.'

`Out,' I corrected.

`Out. Up. I ought to have you court-martialled.'

`Remember,' I said to Old Boy, `don't act the hero. \emph{Be} the hero.'

Old Boy concentrated.

Rain fell at the double and, taking this as a sign, Doogie nodded. We
left the stream and headed up the hill. In places, the ground was uneven
mulch. It blistered and sucked as we crept. My visibility extended less
than five metres. Beyond that, the world was impressionistic. We
progressed in a chimp-like swagger that pickled our legs with lactic
acid.

`We could do with some Agent Orange,' murmured Doogie. `You know, an
exfoliant.'

`You could do with a lobotomy. The word is defoliant. Don't you ever
listen to the science bit?'

`Oh, you're such a---'

`Pacifist?' I offered.

`Pacifists don't recommend lobotomies.'

`Listen you, I've had to take my glasses off because they don't fit
under my visor. That means I can't see diddly.'

`Hmm,' he muttered, sniffing the air.

`When you see somebody, you have to point them out and let me aim along
your arm. It will just be one big blur otherwise. Is that OK?'

`OK,' he replied, sounding distracted. He removed the paintball hopper
and tapped it once against his head. This done, he slammed it back into
the gun. `Now, if we get separated, the watchword is ``pixie''. Repeat,
``pixie''.'

`You're ``irritating'',' I said. `Repeat, ``irritating''.'

Up ahead, where the shrubbery was a battlement of green, we heard two
sounds. The first was someone clearing his throat. The second was
someone being slapped upside the goggles for clearing his throat.

Doogie stopped. I almost walked over him. Old Boy bumped into the back
of me.

The clearing became silent but for the sound of rain.

Doogie crouched and patted the ground. Pinched some moss. Observed its
fall. Sniffed the rainy gusts. Then he looked back at me and held up one
finger, two fingers, and clapped silently. He nodded.

I turned to Old Boy and nodded too.

`Of course,' I whispered, `I have little notion of what that means.'

Before Old Boy could whisper back, a black, fist-sized ball plopped onto
the woodland floor and rolled towards him. As Old Boy took the grenade
and called, `You dropped something,' there was only time for Doogie and
me to dive away.

\emph{Splang!}

This grenade was more explosive than a shaken bottle of Coke. It
detonated with a percussive slap that knocked Old Boy onto his arse. His
chest and legs were yellowed. He rolled downhill and gathered leaves on
his face and chest, glued by the sticky paint. I ran over and pulled him
into the foliage at the edge of the clearing. From this cover, the three
of us had a moment to consider our options. We didn't need long; there
weren't that many options.

Blurred shapes hurried into the clearing and, with chilling calm,
saturated our position with high-velocity plastic. I had no idea what
was camouflage and what was bush. The rounds left their guns with little
fart noises. One hit the exposed flesh of my neck. It hurt. I had to
stop myself walking to the enemy with my hands on my hips, saying, `I'm
sorry, chaps, but that one is going to \emph{bruise}.'

I commando-squirmed towards Doogie.

`They've got more powerful guns than us,' I hissed.

He agreed.

`There are more of them,' I said.

He agreed again.

`Doogie, under the circumstances I would very much prefer not being as
blind as a bat.'

`Roger that,' he said. He vaulted across me, crouched, loosed two
rounds, and fired another volley. Then he dropped onto his back and shot
twice into the sky. He seemed to pause in case a body fell from high
concealment.

`Douglas,' I said, `it would be ideal, really tip-top, if you could
point out those buggers.'

From his supine position, Doogie braced his hands against the ground
either side of his head, put his knees on his chest, and flipped into a
crouch. Fire-fire. Pause. Fire-fire.

`There, there and there.'

Multiple pointing. Brilliant.

For want of something to do, I shouted, `Have it!' and shot Doogie in
the back a couple of times. As he turned, grimacing with pain, I shouted
in his ear, `I think they're flanking us.'

The first casualty of war is innocence.

Poetic justice arrived in pellet form and struck my forehead. It felt
like a door had been closed on my face. I sagged, stunned, to the
ground, and remembered Old Boy, who had already got a grenade in the
chops. I half-focused on his figure. He sat against a nearby tree,
cradling his gun. He had been tarred with paint and feathered with
leaves. `The horror,' he was saying. He caught my eye. `The horror.'

More blurry, camouflaged figures joined the battle. They switched in my
perception from bush to human and back again. The only people I could
identify were the yellow-jacketed marshals on the periphery of the
engagement. I gave one some friendly fire.

`Don't shoot at the marshals!' someone shouted.

Doogie cuffed me on the shoulder.

`There's one.'

He pointed ahead. Much as I appreciated this scrap from Doogie's high
table, there was little to see but greenery. I screamed, `Get
some!'---it seemed apposite---and released several rounds before I
noticed I was shooting a marshal again.

`Don't shoot at the bloody marshals!'

I nodded vigorously, pointed at Doogie, and shrugged.

War is hell.

So we were trapped in a swirling vortex of paint and pain. Our objective
had been to visit all-out war. Have at them; thrash them; rout them. In
short, confirm that they did not, indeed, like it up 'em. This was not
going to happen.

Doogie waved at me.

In reply, I made a shadow-bunny with my left hand.

`That means, ``Get over here'',' he hissed.

I scuttled across to him and crouched at his shoulder.

He fired three blind rounds. `This is just foolery. We're being attacked
from the rear and there's nothing we can do about it.'

`It could be argued that we've passed the foolery stage, Doogie, into
tomfoolery. It's a whole new---'

`If you say ``paintball game'', I'm going to put one of these grenades
down your pants and pull the pin.'

`Point taken.'

`You and Old Boy need to defend the rear. Understood?'

Just then, a barrage of paintballs struck me about the face and groin. I
pitched backwards, dizzy with pain, and collapsed near the tree where
Old Boy was digging into the bedrock of his personality. He grabbed my
collar. `I can hear the gooks talking about us, Andy. They're planning
something.'

`Trust me, you'll be having fun in a minute.'

I was using the term `minute' in same sense as my Dad once used it,
when, looking at the demolished rear wall of our house, said, `In a
minute, when the new extension goes up, you won't recognise the place.'

`Having fun? I'll be---'

Old Boy's reply was lost in a spell of deafness as shots raked my ear. A
second volley tore through the vegetation to either side of us. Old Boy
accepted the pain with dignity at first, but then the final gossamer of
his self-control twanged apart. He screamed, `Medivac!' and threw down
his gun. I watched him disappear into the bushes.

I was beginning to think that drafting him in from the bakery this
morning had not been such a good idea.

I followed him into the undergrowth and became disoriented immediately.
I wanted to head downhill but the ground was uneven and my feet kept
sliding into pools of mud. After more than a minute, I emerged at a
clearing near the stream.

Old Boy stood on the opposite bank. That was good. On my side of the
water was a blurred silhouette that could only belong to Big Jeff. Not
so good.

I moved behind a rotting log and squinted at Big Jeff's gun. It was
unusually large and was pointing at Old Boy's feet.

`Like me gun, dooey? Cussom med. Some pressure on 'un.'

Old Boy, who was born in Nottingham, looked at him blankly. I could
almost hear the machinery inside his head translate and digest the
words.

\emph{`Do you like my gun? It is home made. The pellets can be expelled
with considerable pressure.'}

Jeff fired. The ball left his gun at twice the usual speed and struck
the ground in front of Old Boy, where it threw up soil, leaves and a
mist of yellow. Old Boy stumbled back and almost fell.

I thought, \emph{What would Doogie do?}

`You'm a prisoner of war now, my handsome,' he said to Old Boy. `That
gets us a gurt dollop of points.'

`Um,' said Old Boy. He had seen me and my frantic `keep him talking'
gesture. `Perhaps we should be clear on the relevant points of the
Geneva convention.'

I moved towards Big Jeff until I was close enough to make out two
paintball grenades clipped to his belt. They looked to be a larger type
than the one that had exploded in front of Old Boy. I unhooked
one---gently doing it---but the man stepped backwards, presumably
intending to lead Old Boy away.

`Eh?' he said.

As Jeff turned, I dashed around him and made for Old Boy. Jeff had time
to shoot me in the back twice before I shouted, `Incoming!' and hooked
arms with Old Boy. I kicked up shoulder-high arcs of water as I slewed
through the stream. On the opposite bank, just before we reached the
cover of an old wheelbarrow, I propelled Old Boy over it and made ready
to throw the grenade at Jeff. With luck, it would get us `a gurt dollop
of points'.

As the explosive bag of paint left my fingers, I shrieked a fierce
\emph{kiai} karate scream that Doogie---who had been studying this stuff
years longer than I---had once demonstrated. \emph{Kiai} translates as
`spirit meeting', and the sound begins in the gut, the \emph{hara}, from
where all energy and focus is drawn. The shout represents intense
concentration and the will to overcome all enemies.

However, I bungled the throw, and somehow it hit my big toe.

The main impact was painful enough. This faded. But the following wave
of dull agony made me crumple to the grass. Before I could lie down
fully, Old Boy dragged me behind the wheelbarrow. His face was contorted
in sympathy. `Now, \emph{that} hurt.'

`Too,' I said. `Much. Pain. To. Speak.'

`You daft dapeth,' said Jeff. `Where's 'ee to?'

Somewhere in my excitement-soaked brain, a crinkly bit set to work
unjumbling his words: \emph{`You fool! Where is the explosive device?'}

`With us,' said Old Boy. `Behind the wheelbarrow.'

`Gad, I'll bleddy 'ave 'ee. Put the frickin' pin back in 'un or you'll
be goyn round cockless.'

\emph{`By God, I would very much like to fight you. Disarm it, please,
or suffer the consequent injuries.'}

`Blimey,' sighed Old Boy. `You do it.'

From the corner of a pain-squinted eye, I saw Old Boy take the grenade
and toss it, under-arm, towards Big Jeff---who, for such a large man,
was impressive in his escape reflexes. He crouched and swung his arms
like a sprinter on the `b' of the `bang', but he was too late. The
grenade bounced once, twice, and rolled into the shadow beneath his
outstretched body.

Big Jeff landed with a crunch that could only mean his customised paint
gun had fired its last. His face bounced.

Then the grenade went off.

A supernova of neon-yellow paint sprayed the clearing. It reached Old
Boy and me. Birds left the trees and a second, explosive clap echoed
once off the hills.

`Gad!' Big Jeff screamed.

From piratical earring to Nike air pumps, he had been yellowed but good.

I looked at Old Boy. `Oh.'

`Dear.'

`God.'

Big Jeff moaned into the grass. His arm rose feebly, then fell.

There was a leaf stuck to the paint on Old Boy's chin. I plucked it off.
`Shall we assume that we're about to have a long conversation about the
morals of leaving him versus the physical effort of moving him, and just
run away?'

Old Boy looked horrified. `Leave him here? Without \emph{question}.'

\section*{}

We loped like Transylvanian laboratory assistants back to the scene of
the ambush, but it was deserted. We forged on. At the top of the hill
the trees thinned, and we emerged onto a car park. Big Jeff's ice-cream
van occupied the centre. It was an old Ford Transit with plastic whippy
cones stuck to the corners. Doogie stood to the left of the van. The
ice-cream men stood on the right. Our patrol was covered in yellow
paint. The ice-cream men---who outnumbered us two-to-one---looked minty
fresh. Three marshals in gold jerseys were collecting the guns.

The paintballing had done its evil work: to a man, the warriors stood
akimbo, as though their sexual organs needed separate score sheets for
size. One or two looked like they were smoking cigarettes for the first
time. They murmured with the grave resignation of soldiers expecting
combat flashbacks, wives who hid the steak knives and children who
wanted to know why daddy was living in the tree house. A bit rich, I
thought, considering how easy the victory had been.

`Phew, eh?' I said, laughing too loudly.

Doogie's eyes were difficult to read behind his visor, but his words
destroyed any mystery. `What does it look like? We were basted like
turkeys. Like turkeys.' He licked his ice-cream. `What happened to you
pair?'

`We were protecting the flank.'

`And?'

`There was an---incident,' I said.

`With Big Jeff,' said Old Boy.

`I, for one,' I said, hoping to trump Doogie's indignation with some of
my own, `would have liked to have known that we were playing against Big
Jeff and his'---quieter---`soft-scoop horde.'

`Well,' said Doogie, `you would have run a mile if I'd told you.'

I hesitated, frowning at him. `Precisely.'

`The horror,' said Old Boy. He coughed some paint into a handkerchief.
`Is this toxic?'

`You swallowed some edible paint,' said Doogie. `Big whoop. Try having
paintballs fired at your skull, point blank.'

While we waited in silence for the marshals to confirm the result, one
of the ice-cream men approached. He had long hair and a dainty walk. I
snorted. What a yokel. He stopped with his visor close to mine. He
smelled nice.

`Do you know where Jeff is?' she asked.

`You're a woman,' I said, and the secretarial part of my mind filed the
comment in a drawer marked `This is why you have so little sex'. `Is
that you---you?'

Though most of her face was covered by the mask, her mouth was free. She
grinned. `Hello again.'

Her accent was blank, unplaceable, but there was a Cornish aftertaste to
her words, like water after the rose petals have been removed.

`If you're looking for Jeff,' I said, `he's near the river.'

`Barrington, Tweedie,' she called. `Go and get Jeff, will you? He's down
there.'

`Right away, miss,' said the shorter of the two. They hurried into the
trees.

She turned to me. `Would you like an ice-cream?'

There was nothing to lean casually against. I couldn't flick a hand
through my hair because it was hooded. I fell back on my verbal talents.
`So, ice-cream, eh?'

`Oh,' she said in a disappointed tone. `What happened?'

`Well,' I replied, taken aback. `I, uh, suppose I get nervous around
women.' I waited for her answer. I waited a long time. Then I realised
she was staring over my shoulder. I followed her sightline.

Big Jeff was emerging from the woods. Yellow paint had forced its way
inside his clothes and erupted from his neck, wrists, flies, and ankles.
His boots squelched. His face was grimly set, as though he anticipated
amputation in a field hospital. The moaning skulls of Barrington and
Tweedie had been rammed into Jeff's armpits as impromptu crutches, so
that with each step, the two men seemed to visit the very brink of
quadriplegia.

The rest of the ice-cream men had stopped talking. The marshals were
silent. The air was stretched with pregnant malice like the sticky
camouflage over Big Jeff's belly, but his expression stopped even the
bravest man---paintball-hardened veteran or not---from being the first
to laugh.

It occurred to me that both Old Boy and I had been masked throughout the
episode, and now that we had mixed with Doogie, there would be no way
that Big Jeff could identify us. We just had to keep our mouths shut.

`Hello,' said Old Boy.

\emph{Marvellous.}

Big Jeff removed his mask.

`Oi,' said a marshal. `Masks on until I tell you it's safe to take 'em
off.'

Big Jeff looked at him. This was enough for two of the ice-cream men to
step towards the marshal and fold their arms. The marshal took the hint
and backed away with his hands raised.

Jeff lumbered up to Old Boy. He tapped his fingernail on Old Boy's
visor. Sheepishly, Old Boy moved it up. Those blinking eyes pulled me
back to the cold hour after dawn, when I had dragged him from his
bakery.

\emph{Damn,} I thought. \emph{And blast.}

I pulled up my visor.

`It was me,' I said. `I threw it.'

Big Jeff gurned with malice. `You again.'

I stood there looking at him. My glasses were still in my pocket. Big
Jeff began to blink, but only with his left eye.

Someone coughed delicately. It was a marshal. Now there were three
others with him, and they stood between Big Jeff and the Young
Contemptibles. The tallest marshal said, `Button it up, ladies. I have
to declare a winner. Which of you are the leaders?'

`Him,' said Doogie and I simultaneously.

The marshal escorted me to the ice-cream van. From there he beckoned Big
Jeff, who limped over and stood next me. He was still gurning. The
marshal took our wrists.

`By the powers vested in me, I declare the winner of this morning's
altercation to be Bravo Sub Zero.' He thrust Jeff's arm upward. Applause
dotted the car park like lazy clapping at Sunday afternoon cricket. One
of the marshals took a picture. `Now chuck your masks into this bin.'

Over the next few minutes, we peeled off our greenery and handed back
our guns (except for Doogie; his went back in its adapted drill box, and
then the boot of The Chariot of Phwoar, which he had driven up).
Meanwhile, the ice-cream men loaded the van.

Doogie was polishing his visor near the open boot of his car. I put my
hand on the roof and leaned towards him.

`Doogie,' I said, `did you set this thing up with Big Jeff just for a
laugh?'

`It's a coincidence.'

`Look me in the eye when you say that.'

Doogie raised his eyebrows and tipped his head to one side.

`Well, perhaps not entirely a coincidence.'

I groaned. `Doogie.'

`The name you're looking for,' he said, `is Penelope.'

`Penelope?'

`So,' she said, walking around the car, `you \emph{do} remember me.'

I laughed on reflex. Penelope maintained a half-smile and put her hands
behind her back. She was wearing a sky-blue T-shirt. It stopped above
her belly button, where a piercing twinkled.

`Of course,' I said, `I don't remember you as a fan of paintball. You
were always more of a fan of---'

She looked at me expectantly.

\emph{Blast,} I thought. \emph{She's not filling in the rest of my
sentence.}

I finished it myself with `---the other things.'

Her eyes narrowed.

\emph{Man down. Man very much down.}

`You're right,' she said, skating over the moment. `It's my first time
firing paint pellets. I'm only here to make up the numbers.' She
gestured at the car. `But there seems to be hardly any of you.'

Some distance away, Old Boy shouted, `The Trethewey brothers have the
shits!'

Penelope made a little `o' with her mouth at this fascinating fact.

`Well,' said Doogie, closing the boot, `I thought that was great fun.
And it was good to meet you again, Penelope.'

I scowled at him. If he knew her, why hadn't he said anything?

A xylophonic Greensleeves pealed over the woods. I looked towards the
ice-cream van. The plastic, yellow whippy cones at the corners of the
roof were revolving. Big Jeff was in the driver's seat, beckoning to
Penelope.

`I have to go,' she said.

`Did you think any more about the job?' asked Doogie.

\emph{What job?} I thought.

Penelope began to back away.

`OK,' she said, `we can try you both out and see what you think. Let's
say tomorrow morning at 9 am.'

Doogie nodded at Old Boy, who was walking towards us. He had put on his
white baker's hat. `And our friend?'

`Oh,' she said, passing him, `he can come too. Bye.'

`Hello,' said Old Boy.

\section*{}

Though I could barely be heard over the theme from \emph{Bullitt} and
the frequent double-declutching, I managed to shout, `What's this about
a job?'

`After your run-in with Big Jeff at the Goldie, I went back the next
evening and got talking to Penelope.'

I pulled an exasperated face in the direction of a passing kebab shop.
`This doesn't make any sense. Jeff wants to kill me.'

`It makes perfect sense. If I don't find regular money, soon, then Wade
is going to kick me out. It's alright for you. You're buggering off to
university.'

Doogie emphasised his point with a sharp turn. I braced my foot against
the dashboard. Seat belts in The Chariot of Phwoar existed in the
abstract more than the concrete.

`So Penelope works for Big Jeff?'

`She's his niece.'

`Huh.' I blinked a few times to let this reconfiguration of reality
settle in. `Huh.'

`And,' said Doogie, letting the back-end slip out briefly, `she says a
third of the staff at Brown's have come down with \emph{déjà vu} or
something.'

`\emph{Déjà vu}?'

`Food poisoning,' he said, nodding.

`I'm not a doctor, but I don't think that's what \emph{déjà vu} means.'

`How much will we be paid?' piped up Old Boy, leaning between the two
front seats.

`A shade over minimum wage,' Doogie said. `Well, that's for the drivers.
For you two, it'll be a shade under.'

`What?' said Old Boy.

`Pardon?' I said. `Why I can't I be a driver?'

`What?' said Old Boy.

`Oh,' said Doogie, `let me think of a reason at random.'

`I have a valid licence,' I said, `same as you.'

`And a string of accidents in increasingly cheaper cars. You drive about
as well as I speak French, \emph{amigo}.'

`I'm not being paid under the minimum wage. It's a matter of pride.'

`Nobody is being paid anything yet. We'll find out tomorrow morning if
Big Jeff wants to give us a job or add us to the raspberry ripple.'

`What?' said Old Boy.

In the event, we got the last of the paint out of his ears using some
methylated spirit and a chamois leather.




\end{document}